---
title: "tidy tools"
author: "Mel Moreno"
date: "January 27, 2020"
output: html_document
---


```{r}
# Dependencies

#create_package("~/desktop/cylplot")
#use_mit_license()
#use_r("my_sd")
```



```{r}
x <- 1
f <- function() {
  y <- 2
  z <- 2
  g <- function() {
    z <- 3
    c(x, y, z)
  }
  g()
}
f()

#lexical scoping, if R can't find it in the current environement it will look where it is defined
```

* What's an environment?
heiarchy- every environment has a parent

names-mapping names to objects

collection- 

* How it different to a list?
lists don't have scoping
environments can't have classes
environments have parents


* What's the "default" environment?
* How can you easily see the contents of an environment?

```{r}
library(rlang)

e<-env()
e$a<-1
e$a

e[[1]] #can't get the first variable in an environment

#enviroments have reference semantics

l<- list(a=1)
l$l<-1
str(l)
#lists won't loop because it will create a new environment


```

```{r}
#how to see what's in an environment
#can convert environment to a list
as.list(e)
str(e)


my_sd <- function (x, na.rm = FALSE) {
  sqrt(var(x, na.rm = na.rm))
}
```

```{r}

find_var <- function(name, env) {
  if (env_has(env, name)) {
    env_get(env, name)
  } else {
    find_var(name, env_parent(env))
  }
}


#adding a stop message, so it doesn't keep searching endlessly

find_var <- function(name, env) {
  if (identical(env, empty_env())) {
    stop("Can't find ", name)
  } else if (env_has(env, name)) {
    env_get(env, name)
  } else {
    find_var(name, env_parent(env))
  }
}


find_env <- function(name, env) {
  if (identical(env, empty_env())) {
    stop("Can't find ", name)
  } else if (env_has(env, name)) {
    env
  } else {
    find_env(name, env_parent(env))
  }
}

find_env("var", get_env(sd))
find_env("var", get_env(my_sd))



```

```{r}
get_env(ggplot2::geom_point)
get_env(dplyr::mutate)
get_env(MASS::select)

env_print(MASS::select)
env_parent(MASS::select)
env_parents(MASS::select)
```

```{r}
sqrt_env <- get_env(sqrt)
sqrt_env

env_print(env_parent(my_sd_env))
env_parent(my_sd_env)$var

lobstr::ref(stats::var, env_parent(my_sd_env)$var)

```


```{r}
# `DESCRIPTION` is all about package level.
# `NAMESPACE` is at function leve

# to activate a package, the the usethis::use_package when you are in your function in the package

##conflicted package
## this can help when there are commands in many packages that make a conflict, it makes you pick which version you want to use

# good recommendations to use :: so you know what argument comes from what package
#con is that you can't use a pipe, but you can use @importfrom 
```


```{r}
#usethis::create_package(), to create a new package, don't run in the console
#create_package("~/desktop/cylplot")
#usethis::use_r(), to create a new code for a function
#usethis::use_r("cylsum")
#devtools::load_all(), will load the functions
#devtools::check(), checks if the package is formatted correctly
#usethis::use_mit_license(), add in your license with ""
#devtools::document(), saves the documentation 
#devtools::install(), installing the packages
```

1. check() Note

If you refer to a data-variable inside your functions, preface with a '.data', rlang package

*import '.data' from rlang, make sure it is also in the Description
* Refer to a data variable, 'var': '.data$var'



```{r}
bar_plot <- function(var){
  mtcars +
    ggplot2::geom_bar(ggplot2::aes(.data$var)) +
    ggplot2::coord_flip()
}

# you can also use the [ ] for the user to pass a string

bar_plot <- function(var){
  mtcars +
    ggplot2::geom_bar(ggplot2::aes(.data[var])) +
    ggplot2::coord_flip()
}

#embracing is the solution, the syntax is to look inside the environment variable x and treat the contents like a data variable
bar_plot <- function(var){
  mtcars +
    ggplot2::geom_bar(ggplot2::aes(.data{{var}})) +
    ggplot2::coord_flip()
  
  #embracing the variables in two places with the {{}}, might want to create two arguments taht will control those groupding variables 
  
  hexbin <- function(df, x, y, bins = 10) {
  df %>% 
    ggplot2::ggplot(ggplot2::aes({{ x }}, {{ y }})) + 
    ggplot2::geom_hex(bins = bins)
}
hexbin(diamonds, carat, price)
}


#you can all add the ... to take multiple arguments, instead of making groups for each argument

group_summary <- function(df, x, ...) {
  df %>% 
    group_by(...) %>% 
    summarise(
      n = n(),
      min = min({{ x }}, na.rm = TRUE),
      max = max({{ x }}, na.rm = TRUE)
    )
}
group_summary(mtcars, mpg, cyl, gear)
group_summary(mtcars, mpg, cyl)
```

```{r}
#:: affixes every argument in your function 
#use_package_doc() to create a new file to add the packages being used in the funciton 
#good place to add the packages that are used by all functions
# to stash global roxygen commands

#do not edit the namespace file, roxygen will control it 
#the description is in the control of the user
```


##Interface of the funciton
*interface= outside of a funciton
*implementaiton= inside of a function

Tidyverse design guide
https://design.tidyverse.org

# 9 properties of a function to define its interface
1.name- naming the functions
2.arguments 
- names of the arguments, order as well, putting them in the same name and order if you have it set up
- default values/ required vs optionals
-types
-evaluation (regular, NSE, tidy evaluation)
3.outputs
4.conditions
- errors
-warnings
-messages
5.Side Efffects
-print to console
-making a plot
-io-writing a file
-change the random seed


##Names

1. Functions should be verbs (usually), a doing word
2. Use prefixes to groupt together related functions
3. Use suffizes for variations on a theme
4. Not recommeded to use a "." because many S3 functions use it that are in the base r
5. An arugment should not generally change the type of the output 
6. Most important arguments should come first
7. The data should be the first argument
8. When calling a function, supply data arguments by position; supply detail arguments by name
9. If you use '...', the details should come after
10. Required has no deafult, optional has a default in the description 
11. Normally the ... is passed unto another function, 

```{r}
# when you have a character vector, the default is the first one listed

trimws(x, which = c("both", "left", "right"))

#in developer for dplyr check out the group_by (across({{}}))

```


## type-stability

A property of a function is that the envariance should be simple
Thinking about the error messages and how explanatory they are when you are not entering the correct values
Watch out for functions that return different outputs


```{r}
x<- c(1,2,3,4,5,0,0,0)
y<-mean((x), na.rm= FALSE, trim= 0)
y
```


##including data in a package (S3)

S3- simple, oldest system
S4- more robust but more complicated

#read the chapters in advanced r

```{r}
sloop::otype(tibble::tibble())

#in base r
typeof()

#taking a look at name, row.names, levels and class
attributes()

```

*`print()` looks for the class being inputed and looks for a print for it, it is a generic function
*methods is a specifric implementaiton of a generic function
*methods follows a naming convention:
`{generic}. {class} : t()`
* create a new S3 class to output a user friendly view

```{r}
#will tell you on how it found the method
x<- factor(1:10)
sloop::s3_dispatch(print(x))

#=> print.factor
# * print.default

#the one with the arrow is the one that got called

#exactly the code of the print
sloop::s3_get_method(print.factor)

sloop::s3_get_method(print.table)

sloop::s3_get_method(print.function)

sloop::s3_get_method(print.default)


```

```{r}
#Best practices:
# https://adv-r.hadley.nz/s3.html#s3-classes
#  
```

Much better to create a `bizzaro` generic, then implement methods:

* `create_package("~/desktop/bizzaro")`
* `use_mit_license()`
* `use_r("bizarro")`

```{r}

# Is there are to many if, else statements, then it might be better to make all of the circumstances into their own functions 

#' @export
bizarro <- function(x) {
  # This uses magic to pass arguments to the right method
  UseMethod("bizarro")
}
#' @export
bizarro.character <- function(x) {
  str_reverse(x)
}
str_reverse <- function(x) {
  purrr::map_chr(stringr::str_split(x, ""), 
    ~ stringr::str_flatten(rev(.x))  
  )
}
```

```{r}
bizarro.default <- function(x) {
  stop(
   "Don't know how to make bizzaro <", 
   class(x)[[1]], ">", 
   call. = FALSE 
  )
}
```

```{r}
#' @export
bizarro.numeric <- function(x) {
  -x
}
```

```{r}
#the map is for each column
#' @export
bizarro.data.frame <- function(x) {
  x[] <- purrr::map(x, bizarro)
  setNames(x, bizarro(names(x)))
}
```


```{r}
#will show the method of creating the data
use_data_raw()


```



